Sailing the High Seas:\\ A Christian Exploration of Piracy

### 2024-04-18 paper.tex
add response to malware

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed. Piracy
circumvents mainline distribution channels that may incorporate secure policies
of data integrity, authenticity, and privacy. There are piracy tools and sites
that provide some ways to vet the authenticity of a user based on the user's
previous history and relationship with the piracy community. For example,
ThePirateBay, one of the most popular pirating sites, displays the status or
class of their users and holds these users to higher standards in order to
retain trust with the site's end users.~\cite{suprbay:status} Nevertheless, not
all sites provide these metrics or warnings for the average end-user. Instead,
the burden is often on the end-user, and it is not unfair to assume that the
average person would not be able to analyze downloaded software for malware.

The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by Mezzour et al. reveals that piracy is not equal
around the globe, and it poses serious problems especially for people in
poor countries where piracy is widespread. Although they hypothesized, like
other researchers, that \textcquote{mezzour:empirical-study}[,]{%
  cyber criminals would target rich countries because the monetary benefit of
  compromising rich people's computers is higher
} but they found that, \textcquote{mezzour:empirical-study}[.]{%
  surprisingly, poor countries in Sub-Saharan Africa because of the low cost of
  attacking computers in this region%
} Mezzour et al. conclude that, due to the high correlation between piracy
and malware, one of the policy implications is that Sub-Saharan Africa requires
reducing piracy to combat the spread of malware.
Antivirus provider Kaspersky recently uncovered an example of malware spreading
through pirated software.~\cite{pcmag:malware}

\subsubsection{Response}
An argument based on malware distribution presents a strong case against
piracy. Moreover, we have to acknowledge that the problem targets those with
less resources (whether that be information, financial resources, or technical
resources) to protect themselves from the threats that malware poses.

>>>>

Piracy may openly distribute dangerous illegal content, but arguably the
larger threat is the dangerous content that remains undisclosed. 
The relationship between piracy and malware distribution is not just a
theoretical argument against the use of piracy. Although research has remained
rather theoretical in this area, some researchers have performed empirical
studies to find a stronger link between more prevalent use of piracy and
malware presence. The study by Mezzour et al. reveals that piracy is not equal
around the globe, and it poses serious problems especially for people in
poor countries where piracy is widespread. Although they hypothesized, like
other researchers, that \textcquote{mezzour:empirical-study}[,]{%
  cyber criminals would target rich countries because the monetary benefit of
  compromising rich people's computers is higher
} but they found that, \textcquote{mezzour:empirical-study}[.]{%
  surprisingly, poor countries in Sub-Saharan Africa because of the low cost of
  attacking computers in this region%
} Mezzour et al. conclude that, due to the high correlation between piracy
and malware, one of the policy implications is that Sub-Saharan Africa requires
reducing piracy to combat the spread of malware.
Antivirus provider Kaspersky recently uncovered an example of malware spreading
through pirated software.~\cite{pcmag:malware}

\subsubsection{Response}
An argument based on malware distribution presents a strong case against piracy. Moreover,
we have to acknowledge that the problem targets those with less resources (whether that be
information, financial resources, or technical resources) to protect themselves from the
threats that malware poses. Piracy circumvents mainline distribution channels that may
incorporate secure policies of data integrity, authenticity, and privacy. However, there
are piracy tools and sites that provide some ways to vet the authenticity of a user based
on the user's previous history and relationship with the piracy community. For example,
ThePirateBay, one of the most popular pirating sites, displays the status or class of
their users and holds these users to higher standards in order to retain trust with the
site's end users.~\cite{suprbay:status} Nevertheless, not all sites provide these metrics
or warnings for the average end-user. Instead, the burden is often on the end-user, and
it is not unfair to assume that the average person would not be able to analyze downloaded
software for malware. Thus, to safely make use of piracy tools, one must be aware of the
risks and the ways that they can mitigate those. This is not to say that users need to
reverse engineer all the software they download to look for malicious behavior, but they
do need to be aware of software sources that give them a much better shot at getting an
untainted copy. As mentioned previously, user trust is a crucial component of piracy;
those who choose to enter this domain should be careful to download only from those with a
high reputation in the community---backed by a long time of faithful service.
